Cover letter for the IJRR submission \\ ``An efficient acyclic contact planner for multiped robots''

### 2016-01-20 cover_letter.tex
cover letter

The extension of our work addresses the main comments of the reviewers:

@@

\item The paper has been largely re-written: we provide a clearer
comparison to the state of the art (Section 1.1); we clarify our statement regarding
our computation times (Section 6 and 6.1.6); we make a clear distinction between the
theoretical concepts we propose and their approximation (Section 2).

>>>>

Regarding the conference paper, this apper paper presents new contributions that we first highlight:

\begin{itemize}
\item We introduce a new criterion for asserting the static equilibrium of a robot configuration. It works for arbitrary
legged robots, and handles any kind of contact configurations and surface orientation. It is formulated as a really efficient Linear Program, and 
can be used to compute a value of robustness of the configuration. This robustness is useful for real robots applications, where many uncertainties
in the state estimation of the robot can lead to incorrect evaluations of the equilibrium.
\item We present two new heuristics that we use to bias our contact planner framework towards configurations relevant for the task being performed.
\item We present a complete algorithm for contact planning that integrates the robust equilibrium criterion.
\end{itemize}

The extension of our work also addresses the main comments of the reviewers, and proposes lesser contributions,
that we detail in the following lines.

@@

\item The paper has been largely re-written: we provide a clearer
comparison to the state of the art (Section 1.1); we clarify our statement regarding
our computation times and compare our method with the state of the art (Section 6); we make a clear distinction between the
theoretical concepts we propose and their approximation (Section 2).
